Comprehensive Quality-Aware Automated Semantic Web Service Composition

### 2017-01-25 paper.tex
update two references

\textbf{QoS-aware EC approaches}. Evolutionary Computation techniques are widely used to solve optimisation problems, where the search space is big, so that near-optimised solutions can be found in reasonable time. Genetic Programming (GP) \cite{da2016particle,da2015graphevol} is a typical EC technique applied to automated web service composition. GP-based approaches utilise tree representations, on which service and constructs are represented as terminal nodes and functional nodes respectively. The crossover and mutation operations reproduce various individuals while ensuring the correctness of structure. In \cite{yu2013adaptive}, the author optimises the overall quality of service composition by using a fitness function, which is also liable for the correctness in functionality through penalising infeasible solutions. Also, this paper increase the mutation rate while encountering low diversity in the population and adopt a higher crossover probability while trapped in local optimisation.

@@

To simplify the checking of constraints for solutions, an indirect PSO-based approach was introduced in \cite{da2016particle}. A general graph is used as representation as composite solution in their PSO algorithm considering QoS optimisation. However, this solution does not consider distinguished matchmaking quality, which could lead to over-general outputs to be produced by selected services. In fact, customers' perspectives, application domains and ontology granularity all could have significant impact on the outputs requested by users. In some scenarios, the output is too broad to bear any specific meaning for the customers, even though those web services selected leads to a very good overall QoS. Therefore, we fill the gap by considering different matching types and parameter similarity to determine the overall quality of web service composition. Weighed graphs are also utilised in PSP to facilitate a new representation of web service composition adopted from \cite{da2016particle}.
\section{Problem Description}\label{problemDes}

>>>>

\textbf{QoS-aware EC approaches}. Evolutionary Computation techniques are widely used to solve optimisation problems, where the search space is big, so that near-optimised solutions can be found in reasonable time. Genetic Programming (GP) \cite{da2015graphevol} is a typical EC technique applied to automated web service composition. GP-based approaches utilise tree representations, on which service and constructs are represented as terminal nodes and functional nodes respectively. The crossover and mutation operations reproduce various individuals while ensuring the correctness of structure.

Gupta et al. \cite{gupta2015optimization} proposed an improved Genetic Algorithm for QoS-ware web service composition, where some population associated with lower fitness are discarded with bringing in new offerings in each generation.

In \cite{yu2013adaptive}, the author optimises the overall quality of service composition by using a fitness function, which is also liable for the correctness in functionality through penalising infeasible solutions. Also, this paper increase the mutation rate while encountering low diversity in the population and adopt a higher crossover probability while trapped in local optimisation.

A promising GraphEvol is proposed in \cite{da2015graphevol}, where web service composition are in a form of Directed Acyclic Graph(DAG) employing Graph-based evolutionary operators like crossover and mutation.

@@

To simplify the checking of constraints for solutions, an indirect PSO-based approach was introduced in \cite{da2016particle}. A general graph is used as representation as composite solution in their PSO algorithm considering QoS optimisation.

Other non-EC techniques are also introduced in QoS-ware web service composition. A heuristic service composition method is proposed by Tang et al. \cite{qi2010combining} proposed,  named local optimisation and enumeration, which is to filter a small number of promising candidates related to each task by local selection, and all the composite solutions are enumerated to reach the near-to-optimal.

However, composite solutions from \cite{qi2010combining,da2016particle,ma2015hybrid,da2015graphevol,yu2013adaptive} does not consider distinguished matchmaking quality in their fitness function, which might lead to over-general outputs to be produced by selected services, The finding is evidently supported by comparing two different evaluation model in Sect. \ref{comparisonTest}. In fact, customers' perspectives, application domains and ontology granularity all could have significant impact on the outputs requested by users. In some scenarios, the output is too broad to bear any specific meaning for the customers, even though those web services selected leads to a very good overall QoS. Therefore, we fill the gap by considering different matching types and parameter similarity to determine the overall quality of web service composition. Weighed graphs are also utilised in PSP to facilitate a new representation of web service composition adopted from \cite{da2016particle}.
\section{Problem Description}\label{problemDes}
